### 2021-03-17 paper.Rmd
shuffling and add references
section headings

- Bases notation (Sherry)

@@

- Display (Sherry)

@@

- Choosing targets, inc pp indexes (Sherry)

@@

- Geodesic interpolation (Ursula)

@@

- Slices vs projections (Ursula)

@@

- Transformations on projections (Ursula)

@@

<!-- needs to be shortend -->

@@

Tasks such as the identification of outlying points or cluster analysis can be performed visually using the tour. Here, a "spin-and-brush" approach works well, since different views will reveal different features and a persistent brush helps us to connect this to the previously observed information. As an example we briefly summarize an analysis from @Cook2007-be that explores clustering of the physics data previously used to in the context of projection pursuit [@Friedman1974-ck; @Cook1995-ae]. This data is well described by its geometric structure: a two-dimensional triangle with two one-dimensional strands linearly extending in different directions from each vertex. These strands can sequentially be identified as clusters using the spin-and-brush approach, as shown in Fig. \ref{prim7-tour}. We stop the tour each time a cluster is clearly separate from the main distribution in the current projection and brush the points in a new color. In the end the full structure becomes apparent and can be visualized by replaying the tour with all clusters highlighted in different colors.

@@

- spinifex (Nick)

@@

- liminal (Stuart)

The liminal R package uses the tour to explore the quality of non-linear dimensionality reduction algorithms. The interface consists of two side by side views consisting of a scatter plot displaying a reduced form of the data, and an interactive tour. Controls such as play/stop/restart are implemented allowing a user to pause on interesting projections and return them to their R session for further analysis. Linked brushing is implemented on both views - if a users brush on the scatter plot view they can see if and how an algorithm like t-SNE has distorted distances in higher dimensional space, while if they brush on the tour view, the tour is paused and structure like cluster separation can be ascertained.

- python (Di to follow up with Csaba)

@@

- Model vis examples eg random forest (from Hadley, removing the blindfold) (Natalia)

@@

- Physics (Ursula)

@@

\begin{figure*}
  \centering
           \includegraphics[width=0.45\textwidth]{figures/allcenter-301.png}
         \includegraphics[width=0.45\textwidth]{figures/jetCluster-027.png}

\caption{Selected frames from using a grand tour of the physics data. Left: the three different types of measurements (shown in different colors) are aligned along different directions in parameter space. Right: an outlying point is marked with an asterisk symbol in the ATLAS7new facet.}
\label{fig:physics}
\end{figure*}

- Bioinformatics (Stuart)

@@

@@

> figure 15

- neural networks (this could go into model vis?)

>>>>

## Notation

@@

## Display

@@

## Finding targets

@@

## Geodesic interpolation

@@

## Slices, sections and projections

@@

## Transformations on projections

@@

<!-- needs to be shortened -->

@@

Tasks such as the identification of outlying points or cluster analysis can be performed visually using the tour. Here, a "spin-and-brush" approach works well, since different views will reveal different features and a persistent brush helps us to connect this to the previously observed information. As an example we briefly summarize an analysis from @Cook2007-be that explores clustering of the physics data previously used to in the context of projection pursuit [@Friedman1974-ck; @Cook1995-ae]. This data is well described by its geometric structure: a two-dimensional triangle with two one-dimensional strands linearly extending in different directions from each vertex. These strands can sequentially be identified as clusters using the spin-and-brush approach, as shown in Figure \ref{prim7-tour}. We stop the tour each time a cluster is clearly separate from the main distribution in the current projection and brush the points in a new color. In the end the full structure becomes apparent and can be visualized by replaying the tour with all clusters highlighted in different colors.

@@

@@

The liminal R package uses the tour to explore the quality of non-linear dimensionality reduction algorithms [@Lee2020-kg]. The interface consists of two side by side views consisting of a scatter plot displaying a reduced form of the data, and an interactive tour. Controls such as play/stop/restart are implemented allowing a user to pause on interesting projections and return them to their R session for further analysis. Linked brushing is implemented on both views - if a users brush on the scatter plot view they can see if and how an algorithm like t-SNE has distorted distances in higher dimensional space, while if they brush on the tour view, the tour is paused and structure like cluster separation can be ascertained.

- other work (Di)

@@

## Model Visualization

- Model vis examples eg random forest (from Hadley, removing the blindfold) (Stuart)

@@

## Physics

@@

\begin{figure*}
  \centering
           \includegraphics[width=0.45\textwidth]{figures/allcenter-301.png}
         \includegraphics[width=0.45\textwidth]{figures/jetCluster-027.png}
\caption{Selected frames from using a grand tour of the physics data. Left: the three different types of measurements (shown in different colors) are aligned along different directions in parameter space. Right: an outlying point is marked with an asterisk symbol in the ATLAS7new facet.}
\label{fig:physics}
\end{figure*}

## Bioinformatics

@@

## Geometry of data

@@
